SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios

### 2015-10-20 papers/B1555_EdgeOn/B1555_letter.tex
update for key words
try to fix pdf
update disc lens ratio in draft

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\begin{keywords}
gravitational lensing -- quasars: individual CLASS B1555+375 -- cosmology: observations 
\end{keywords}

@@

\begin{figure}
\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
\caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375. The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dashed line. The position of the source is at ($-0.1953$, $-0.1494$), which is marked by the red filled circle. The centroid positions of the two mass components of the lens (an SIE and an exponential disc) are marked by the black filled triangles.}
\label{fig:model}
\end{figure}

@@

Our results for B1555+375 clearly demonstrate that a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies. While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies. We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution may a significant source of bias.

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{aecompl}

@@

\begin{keywords}
gravitational lensing -- quasars: individual CLASS B1555+375 -- galaxies: structure 
\end{keywords}

@@

\begin{figure}
%\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
\includegraphics[width=72mm]{gravlens_exp_try5_plot-2.eps}
%\includegraphics[width=72mm]{fig2_twocontour_b.eps}
\caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375. The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dashed line. The position of the source is at ($-0.1953$, $-0.1494$), which is marked by the red filled circle. The centroid positions of the two mass components of the lens (an SIE and an exponential disc) are marked by the black filled triangles.}
\label{fig:model}
\end{figure}

@@

Our results for B1555+375 clearly demonstrate that a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies. We've seen 5 out of 25 SHARP lenses revealing a disc in AO imaging, which these lenses are source selected thus less possible to be biased (Fassnacht et al., in prep.). While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies. We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution may a significant source of bias.
